%testsdadasfasd
\subsection{Preliminary surface energy measurement}
There are currently no experimental methods available to measure surface energies associated with different crystallographic orientations of metals. High temperature methods involving cylindrical metal samples and destructive methods involving drop shape samples of a targeted liquid metal near the melting point are available for measuring surface energy of amorphous and isotropic solid metals.\cite{Egry2010,Aqra2011,Cao2011} For our research, however, we require knowledge of orientation-, morphology- and composition-dependent surface energies for validation of DFT results and for use in abnormal grain growth simulations. For glass and polymeric solids with relatively low surface energies, the water-drop method has been shown to be effective for the determination of surface energy at room temperature.\cite{Ahadian2010,Kwok2000,Tavana2005} We attempted to use this approach for contact angle measurements on large 17.9$\%$Ga Galfenol single crystal samples with \hkl(001), \hkl(011) and \hkl(111) grains with facilities at NIST. Results from this experiment were inconclusive because a large range of \ca[s] were measured for each single-crystal surface. This was most likely due to oxidation on the Galfenol surface causing a non-ideal, non-pristine surface. These results are also inconsistent with the predicted outcome of water completely wetting the high-energy surface, which may be a result of the sample roughness. While each sample may have been polished using silica gel with 60 nm particles,\cite{Costa2016} there could have been enough roughness at the droplet location to trap the triple-phase boundary and cause higher \ca[s] than expected. 


%\textcolor{red}{\textbf{INCORRECT STATEMENT}: However, non-physical trends in the results lead to the conclusion that disruption of strong inter-atomic and molecular bonds with high coordination numbers at the free substrate surface (an intrinsic property of a metal substrate[75,76,77]) interfered with the water drop surface tension and resultant water drop-substrate contact angles.}


The interactions of water with a low-energy and high-energy solid surface differ significantly. The relative energy of a solid compared to a liquid has to do with the bulk nature of the solid. Solids with weak molecular crystals (e.g., fluorocarbons, hydrocarbons, etc.) where the molecules are held together essentially by physical forces (e.g., van der Waals and hydrogen bonds). Since these solids are held together by weak forces, a very low input of energy is required to break them, thus they are termed “low energy” and typically have surface energy $<$70 mJ/m$^2$.  Metals, glasses, and ceramics are known as "hard solids" because the chemical bonds that hold them together (e.g., covalent, ionic, or metallic) are very strong. Thus, these surfaces are high-energy because of the high amount of energy needed to break these solids to make two new surfaces, as mentioned in Section \ref{define-surf-energy}. High energy solids typically have surfaces energies $>$100 mJ/m$^2$.  The threshold between these two types of surfaces lies in their surface energy values relative to the surface tension of water, $\sim$72 mJ/m$^2$. Water tends to partially wet a low energy surface and completely wet a high energy surface based on how much lesser or greater the surface energy of the solid is compared to water, respectively. 

I will investigate two approaches to overcome the challenges involved in measuring the surface energy of metals using contact angle measurements. The first will 

Gallium is a liquid with a very high surface tension, $\sim$715.3 mJ/m$^2$, at room temperature compared to water. 

We proposed using a liquid gallium droplet to measure the orientation-dependent surface energy of high-surface energy metals, like Galfenol and Alfenol. This is because gallium is a liquid at room temperature with a surface tension of This project has been funded by the \NSF. 

\input{Subfiles/2-1_derive_ga_tech}


\subsection{Experimental Versions}
%todo: Go through each version, and mark what was improved upon from experimental progression. 
\input{Subfiles/2-2_experimental-versions}

%\subsection{Results and Presentations}

%TODO: Explain why this method is not possible from a fundamental thermodynamic position (ie using one thermodynamic equilibirum and plugging it in to another equation at thermodynamic equilibrium). Should be able to go from one thermodynamic equilibrium equation to another, but that is not the case here. The method could still be feasible if more terms (\gamSL between liquid-Ga and solid) were known
